\TheTitle

### 2017-07-14 paper/study.tex
editing summarization results

Table~\ref{tab:cross_commit_results} shows whether the merge-tree size
has an effect on the three studied metrics. An interesting observation
from the figure is that the corrected for T5 and T9 are effected by the
size of the merge-tree, but the accuracy is not. The correctness results
for T5 and T9 are shown in Figure~\ref{fig:correctness_t5_t9}, and the
timing results for T7 are shown in Figure~\ref{fig:timing_t7}.

@@

\begin{itemize}
  \item T4

    \textbf{Correctness:}
    The $\chi^2$ statistic is $13.07$ with a p-value of $0.0003$.
    $13.07 > 3.841$ and $0.0003 < 0.05$, therefore we reject the null
    hypothesis.
    \vspace{2mm}
    \begin{tabular}{cc|rr}
                            &           & \multicolumn{2}{c}{Linvis}\\
                            &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk} & Correct   & 6                            & 0\\
                            & Incorrect & 15                           & 2\\
    \end{tabular}
    \vspace{3mm}

@@

  \item T5

    \textbf{Correctness:}
    The correctness results are split for this task. For \comA, the
    $\chi^2$ statistic is $5.14$ with a $p-value$ of $0.02334$. $5.14 >
    3.841$ and $0.02334 < 0.05$, therefore we reject the null
    hypothesis.
    \vspace{2mm}
    \begin{tabular}{cc|rr}
                             &           & \multicolumn{2}{c}{Linvis}\\
                             &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}  & Correct   & 4                            & 0\\
                             & Incorrect & 7                            & 0\\
    \end{tabular}
    \vspace{3mm}

    The $\chi^2$ statistic for \comB is $5.14$ with a p-value of
    $0.02334$. $4.14 > 3.841$ and $0.02334 < 0.05$, therefore we reject
    the null hypothesis.
    \vspace{2mm}
    \begin{tabular}{cc|rr}
                             &           & \multicolumn{2}{c}{Linvis}\\
                             &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}  & Correct   & 1                            & 0\\
                             & Incorrect & 7                            & 4\\
    \end{tabular}
    \vspace{3mm}

    While there is a difference in correctness between different-sized
    merge-trees, \tool improves correctness of determining the other
    commits related to a commit in trees of varying sizes.

@@

  \item T6

    \textbf{Correctness:}
    The $\chi^2$ statistic is $14.06$ with a p-value of $0.0002$.
    $14.06 > 3.841$ and $0.0002 < 0.05$, therefore we reject the null
    hypothesis.
    \vspace{2mm}
    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk} & Correct   & 5                            & 0\\
      & Incorrect & 16                           & 2\\
    \end{tabular}
    \vspace{3mm}

@@

  \item T7

    \textbf{Correctness:}
    The $\chi^2$ statistic is $11.07$ with a p-value of $0.0009$.
    $11.07 > 3.841$ and $0.0009 < 0.05$, therefore we reject the null
    hypothesis.
    \vspace{2mm}
    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk} & Correct   & 8                            & 0\\
      & Incorrect & 13                           & 2\\
    \end{tabular}\\
    \vspace{3mm}

@@

    \textbf{Timing:} The null hypothesis is not rejected in the case of
    \comA, but is rejected in the case of \comB. This indicates that
    \tool is able to help users determine who made the most
    contributions to a merge in a large tree than in a small tree.

    Overall, \tool improves the correctness for trees of various sizes,
    but only has an effect on the amount of time taken when the tree is
    large.

  \item T8

    \textbf{Correctness:}
    The $\chi^2$ statistic is $13.07$ with a p-value of $0.0003$.
    $13.07 > 3.841$ and $0.0003 < 0.05$, therefore we reject the null
    hypothesis.
    \vspace{2mm}
    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk} & Correct   & 6                            & 0\\
      & Incorrect & 15                           & 2\\
    \end{tabular}\\
    \vspace{3mm}

@@

    \textbf{Timing:} The p-value is 0.0009, which is less than 0.05; we
    reject the null hypothesis. The delta estimate is -0.57, indicating
    a large effect size.

  \item T9

    \textbf{Correctness:}
    The correctness results are split for this task. For \comA, the
    $\chi^2$ statistic is $4.17$ with a p-value of $0.0412$. $4.17 >
    3.841$ and $0.0412 < 0.05$, therefore we reject the null hypothesis.
    \vspace{2mm}
    \begin{tabular}{cc|rr}
                             &           & \multicolumn{2}{c}{Linvis}\\
                             &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}  & Correct   & 5                            & 0\\
                             & Incorrect & 6                            & 0\\
    \end{tabular}
    \vspace{3mm}

    The $\chi^2$ statistic for \comB is $6.125$ with a p-value of
    $0.0133$. $6.125 > 3.841$ and $0.0133 < 0.05$, therefore we reject
    the null hypothesis.
    \vspace{2mm}
    \begin{tabular}{cc|rr}
                             &           & \multicolumn{2}{c}{Linvis}\\
                             &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}  & Correct   & 1                            & 0\\
                             & Incorrect & 8                            & 3\\
    \end{tabular}
    \vspace{3mm}

@@

  \item T10

    \textbf{Correctness:}
    The $\chi^2$ statistic is $4$ with a p-value of $0.0455$.
    $4 > 3.841$ and $0.0455 < 0.05$, therefore we reject the null
    hypothesis. The p-value is very close to the $\alpha$ value in this
    case, so the conclusion is not as well defined.
    \vspace{2mm}
    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}   & Correct   & 14                           & 1\\
      & Incorrect & 8                            & 0\\
    \end{tabular}
    \vspace{3mm}

    \textbf{Accuracy:} The null hypothesis is rejected; the delta
    estimate is -0.35, indicating a medium effect size. \tool provides
    an improvement in accuracy when determining which modules are
    involved with a merge.

>>>>

Table~\ref{tab:cross_commit_results} shows whether the merge-tree size
has an effect on the three studied metrics. An interesting observation
from the figure is that the correctness for T5 and T9 are effected by
the size of the merge-tree, but the accuracy is not. The correctness
results for T5 and T9 are shown in Figure~\ref{fig:correctness_t5_t9},
and the timing results for T7 are shown in Figure~\ref{fig:timing_t7}.

@@

\begin{itemize}
  \item \emph{T4}: What is the series of merges involved with merging this
    commit?

    \textbf{Correctness:}
    The $\chi^2$ statistic is $13.07$ with a p-value of $0.0003$.
    $13.07 > 3.841$ and $0.0003 < 0.05$, therefore we reject the null
    hypothesis.

    \vspace{2mm}
    \begin{tabular}{cc|rr}
                            &           & \multicolumn{2}{c}{Linvis}\\
                            &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk} & Correct   & 6                            & 0\\
                            & Incorrect & 15                           & 2\\
    \end{tabular}
    \vspace{3mm}

@@

  \item \emph{T5}: What other commits are merged with this commit?

    \textbf{Correctness:}
    The correctness results are split for this task. For \comA, the
    $\chi^2$ statistic is $5.14$ with a $p-value$ of $0.02334$. $5.14 >
    3.841$ and $0.02334 < 0.05$, therefore we reject the null
    hypothesis.

    \vspace{2mm}
    \begin{tabular}{cc|rr}
                             &           & \multicolumn{2}{c}{Linvis}\\
                             &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}  & Correct   & 4                            & 0\\
                             & Incorrect & 7                            & 0\\
    \end{tabular}
    \vspace{3mm}

    The $\chi^2$ statistic for \comB is $5.14$ with a p-value of
    $0.02334$. $4.14 > 3.841$ and $0.02334 < 0.05$, therefore we reject
    the null hypothesis.

    \vspace{2mm}
    \begin{tabular}{cc|rr}
                             &           & \multicolumn{2}{c}{Linvis}\\
                             &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}  & Correct   & 1                            & 0\\
                             & Incorrect & 7                            & 4\\
    \end{tabular}
    \vspace{3mm}

    While there is a difference in correctness between different-sized
    merge-trees, \tool improves correctness of determining the other
    commits related to a commit in trees of varying sizes. The
    difference in the two commits stem from the participants that did
    not change outcomes between the tools.

@@

  \item \emph{T6}: How many authors are involved in this merge?

    \textbf{Correctness:}
    The $\chi^2$ statistic is $14.06$ with a p-value of $0.0002$.
    $14.06 > 3.841$ and $0.0002 < 0.05$, therefore we reject the null
    hypothesis.

    \vspace{2mm}
    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk} & Correct   & 5                            & 0\\
      & Incorrect & 16                           & 2\\
    \end{tabular}
    \vspace{3mm}

@@

  \item \emph{T7}: Who contributed the most changes to this merge?

    \textbf{Correctness:}
    The $\chi^2$ statistic is $11.07$ with a p-value of $0.0009$.
    $11.07 > 3.841$ and $0.0009 < 0.05$, therefore we reject the null
    hypothesis.

    \vspace{2mm}
    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk} & Correct   & 8                            & 0\\
      & Incorrect & 13                           & 2\\
    \end{tabular}\\
    \vspace{3mm}

@@

    \textbf{Timing:} The null hypothesis is not rejected in the case of
    \comA, but is rejected in the case of \comB. This indicates that
    \tool is able to help users determine who made the most
    contributions to a merge in a large tree but not in a small tree.

    Overall, \tool improves the correctness for trees of various sizes,
    but only has an effect on the length of time taken when the tree is
    large.

  \item \emph{T8}: How many files were modified in this merge?

    \textbf{Correctness:}
    The $\chi^2$ statistic is $13.07$ with a p-value of $0.0003$.
    $13.07 > 3.841$ and $0.0003 < 0.05$, therefore we reject the null
    hypothesis.

    \vspace{2mm}
    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk} & Correct   & 6                            & 0\\
      & Incorrect & 15                           & 2\\
    \end{tabular}\\
    \vspace{3mm}

    \tool improves the correctness of users when determining the number
    of files that were modified in a merge.

@@

    \textbf{Timing:} The p-value is 0.0009, which is less than 0.05; we
    reject the null hypothesis. The delta estimate is -0.57, indicating
    a large effect size. \tool decreases the time taken to determine the
    number files modified in a merge.

    Overall, \tool assists users to determine the number of files
    modified in a merge more quickly and accurately.

  \item \emph{T9}: Which file(s) had the most changes in this merge?

    \textbf{Correctness:}
    The correctness results are split for this task. For \comA, the
    $\chi^2$ statistic is $4.17$ with a p-value of $0.0412$. $4.17 >
    3.841$ and $0.0412 < 0.05$, therefore we reject the null hypothesis.

    \vspace{2mm}
    \begin{tabular}{cc|rr}
                             &           & \multicolumn{2}{c}{Linvis}\\
                             &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}  & Correct   & 5                            & 0\\
                             & Incorrect & 6                            & 0\\
    \end{tabular}
    \vspace{3mm}

    The $\chi^2$ statistic for \comB is $6.125$ with a p-value of
    $0.0133$. $6.125 > 3.841$ and $0.0133 < 0.05$, therefore we reject
    the null hypothesis.

    \vspace{2mm}
    \begin{tabular}{cc|rr}
                             &           & \multicolumn{2}{c}{Linvis}\\
                             &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}  & Correct   & 1                            & 0\\
                             & Incorrect & 8                            & 3\\
    \end{tabular}
    \vspace{3mm}

    While there is a different in correctness between different-sized
    \mt{s}, \tool improves the correctness when determining which files
    had the most changes in trees of varying sizes. The difference in
    the two commits stem from the participants that did not change
    outcomes between tools.

@@

  \item \emph{T10}: Which modules does this \mt involve?

    \textbf{Correctness:}
    The $\chi^2$ statistic is $4$ with a p-value of $0.0455$.
    $4 > 3.841$ and $0.0455 < 0.05$, therefore we reject the null
    hypothesis. The p-value is very close to the $\alpha$ value in this
    case, so the conclusion is not as well defined.

    \vspace{2mm}
    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}   & Correct   & 14                           & 1\\
      & Incorrect & 8                            & 0\\
    \end{tabular}
    \vspace{3mm}

    \tool improves correctness when determining the modules involved at
    a merge.

    \textbf{Accuracy:} The null hypothesis is rejected; the delta
    estimate is -0.35, indicating a medium effect size. \tool improves
    accuracy when determining which modules are involved with a merge.
